Computational methods in landscape ecology

### 2024-09-20 Sections/04-sampling.qmd
cleans samping

Software to perform multi-scale analysis include the R package multilandr [@Huais2024], ZonalMetrics [@Adamczyk2017] or PyLandStats [@Bosch2019PyLandStatsOpensource] libraries in Python. TODO: add more?

@@

TODO: I do not know if we want to measure software that is less landscape ecology centric/more general spatial analysis. If so, please complete the packages (based on [@Beale2010] I found glmm for R as well as SAS and Stata, but you probably know more about it, especially for R).
Software to conduct diagnostics of spatial autocorrelation include PySAL [@Rey2007]. Mixed effects models are available in the statsmodels [@Seabold2010] and PySAL [@Rey2007] libraries in Python. Spatial weights based on kernel functions can be computed using the PySAL [@Rey2007] library in Python.

>>>>

Software to perform multi-scale analysis include the R package multilandr [@Huais2024], ZonalMetrics [@Adamczyk2017] or PyLandStats [@Bosch2019PyLandStatsOpensource] libraries in Python. 
<!-- TODO: add more? -->

@@

<!-- TODO: I do not know if we want to measure software that is less landscape ecology centric/more general spatial analysis. If so, please complete the packages (based on [@Beale2010] I found glmm for R as well as SAS and Stata, but you probably know more about it, especially for R). -->
Software to conduct diagnostics of spatial autocorrelation include PySAL [@Rey2007]. Mixed effects models are available in the statsmodels [@Seabold2010] and PySAL [@Rey2007] libraries in Python. 
Spatial weights based on kernel functions can be computed using the PySAL [@Rey2007] library in Python.
